---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# success

<!-- badges: start -->
<!-- badges: end -->

The goal of the \pkg{success} package is to allow easy applications of continuous time CUSUM procedures on survival data. Specifically, the Biswas \& Kalbfleisch CUSUM (2008) and the CGR-CUSUM (2021).

Besides this, it allows for the construction of the Binary CUSUM chart and funnel plot on survival data as well.

## Installation

You can install the released version of success from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("success")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("d-gomon/success")
```
## CGR-CUSUM Example

This is a basic example which shows you how to construct a CGR-CUSUM chart on a hospital from the attached data set "surgerydat":
```{r echo = FALSE, warning = FALSE, error = FALSE, message = FALSE}
library(success)
library(survival)
```

```{r success}
dat <- subset(surgerydat, unit == 1)
exprfit <- as.formula("Surv(survtime, censorid) ~ age + sex + BMI")
tcoxmod <- coxph(exprfit, data = surgerydat)

cgr <- cgr_cusum(data = dat, coxphmod = tcoxmod, stoptime = 200)
plot(cgr)
```

You can plot the figure with control limit $h = 10$ by using:
```{r}
plot(cgr, h = 10)
```

And determine the runlength of the chart when using control limit $h = 10$:
```{r}
runlength(cgr, h = 10)
```

Hospital 1 would be detected by a CGR-CUSUM with control limit $h = 10$ after $151$ days.


Alternatively, you can construct the CGR-CUSUM only until it crosses control limit $h = 10$ by:
```{r}
cgr <- cgr_cusum(data = dat, coxphmod = tcoxmod, h = 10)
plot(cgr)
```

## References

The theory behind the methods in this package can be found in:

Gomon D., Putter H., Nelissen R.G.H.H., van der Pas S (2022): [CGR-CUSUM: A Continuous time Generalized Rapid Response Cumulative Sum chart](https://doi.org/10.48550/arXiv.2205.07618), *arXiv: a preprint*



